Verifying Demonstrations

### 2018-08-23 paper/adversary-model.tex
Fixes label for witness-adv def, removes treated comment

\begin{definition}[Strongest witness adversary]
  Things are the same as in \cref{base-witness-adversary}, except that \(S\) 
  learns the witness' identity \(W\).
\end{definition}

>>>>

\begin{definition}[Strongest witness adversary]%
  \label{strongest-witness-adversary}
  Things are the same as in \cref{base-witness-adversary}, except that \(S\) 
  learns the witness' identity \(W\).
\end{definition}
